---
title: "AS3-2: 股市動態"
author: "第 八 組"
date: "`r Sys.time()`"
output:
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)
```
<hr>

**股票動態**

股票市場是買賣雙方交易公司股票的地方，也是個人和公司投資的最受歡迎的方式之一。現在估計世界股票市場規模達到數兆。紐約證券交易所位於紐約市，是世界上最大的股票市場。 紐約證券交易所約有2,800家上市公司。在這個問題上，我們將看看其中五家公司的每月股價：IB、通用電氣（GE）、寶潔、可口可樂和波音。此問題中使用的數據來自Infochimps。

使用`read.csv()`下載並讀取以下文件：

+ `data/IBMStock.csv`
+ `data/GEStock.csv`
+ `data/ProcterGambleStock.csv`
+ `data/CocaColaStock.csv`
+ `data/BoeingStock.csv` 

分別存入資料框`IBM`、`GE`、`ProcterGamble`、`CocaCola`和`Boeing`，
每個資料框都有兩個變量，描述如下：

+ `Date`：日期
+ `StockPrice`：給定月份公司的平均股價

在這個案例，我們將看看這些公司的股票動態如何隨著時間的推移而發生變化。

<br><hr>

###  Section-1 Summary Statistics

__§ 1.1__ Our five datasets all have the same number of observations. How many observations are there in each data set?
```{r}
D_IBM = read.csv("data/IBMStock.csv", stringsAsFactors=F)
nrow(D_IBM)
```

為了慎重起見，另外四間公司也一併驗證。
```{r}
D_GE = read.csv("data/GEStock.csv", stringsAsFactors=F)
nrow(D_GE)
D_PG = read.csv("data/ProcterGambleStock.csv", stringsAsFactors=F)
nrow(D_PG)
D_CC = read.csv("data/CocaColaStock.csv", stringsAsFactors=F)
nrow(D_CC)
D_B = read.csv("data/BoeingStock.csv", stringsAsFactors=F)
nrow(D_B)
D_B$company=as.factor("B")
D_CC$company=as.factor("CC")
D_GE$company=as.factor("GE")
D_IBM$company=as.factor("IBM")
D_PG$company=as.factor("PG")
alldata = rbind(D_B,D_CC,D_GE,D_IBM,D_PG)
```


__§ 1.2__ What is the earliest year in our datasets?
```{r}
D_B$Date = as.Date(D_B$Date, format="%m/%d/%y")
D_CC$Date = as.Date(D_CC$Date, format="%m/%d/%y")
D_GE$Date = as.Date(D_GE$Date, format="%m/%d/%y")
D_IBM$Date = as.Date(D_IBM$Date, format="%m/%d/%y")
D_PG$Date = as.Date(D_PG$Date, format="%m/%d/%y")
alldata$Date = as.Date(alldata$Date, format="%m/%d/%y")
min(D_IBM$Date)
```

__§ 1.3__ What is the latest year in our datasets?
```{r}
max(D_IBM$Date)
```

__§ 1.4__ What is the mean stock price of IBM over this time period?
```{r}
mean(D_IBM$StockPrice)
```

__§ 1.5__ What is the minimum stock price of General Electric (GE) over this time period?
```{r}
min(D_GE$StockPrice)
```

__§ 1.6__ What is the maximum stock price of Coca-Cola over this time period?
```{r}
max(D_CC$StockPrice)
```

__§ 1.7__ What is the median stock price of Boeing over this time period?
```{r}
median(D_B$StockPrice)
```

__§ 1.8__ What is the standard deviation of the stock price of Procter & Gamble over this time period?
```{r}
sd(D_PG$StockPrice)
```

<br><hr>

###  Section-2 Visualizing Stock Dynamics

__§ 2.1__ Around what year did Coca-Cola has its highest stock price in this time period? Around what year did Coca-Cola has its lowest stock price in this time period?
```{r}
plot(D_CC$Date , D_CC$StockPrice, type = "l", xlab = ("Date") , ylab = ("StockPrice"))
abline(v = D_CC$Date[which.max(D_CC$StockPrice)], col = "blue")
abline(v = D_CC$Date[which.min(D_CC$StockPrice)], col = "blue")
D_CC$Date[which.max(D_CC$StockPrice)]
D_CC$Date[which.min(D_CC$StockPrice)]
```
#1973
#1980

__§ 2.2__ In March of 2000, the technology bubble burst, and a stock market crash occurred. According to this plot, which company's stock dropped more?

```{r}
plot(D_CC$Date[301:432] , D_CC$StockPrice[301:432], type = "l", col="black" , ylim = c(0 , 200) , xlab = ("Year") , ylab = ("StockPrice"))
lines(D_B$Date[301:432] , D_B$StockPrice[301:432], type = "l", col="red" , ylim = c(0 , 200))
lines(D_GE$Date[301:432] , D_GE$StockPrice[301:432], type = "l", col="brown" , ylim = c(0 , 200))
lines(D_IBM$Date[301:432] , D_IBM$StockPrice[301:432], type = "l", col="orange" , ylim = c(0 , 200))
lines(D_PG$Date[301:432] , D_PG$StockPrice[301:432], type = "l", col="green" , ylim = c(0 , 200))
abline(v = as.Date("2000-03-01") , col = "blue")
```
#General Electric (GE)

__§ 2.3__ (a) Around 1983, the stock for one of these companies (Coca-Cola or Procter and Gamble) was going up, while the other was going down. Which one was going up? 
```{r}
plot(D_CC$Date[96:228] , D_CC$StockPrice[96:228], type = "l", col="black", xlab = ("Date") , ylab = ("StockPrice"))
lines(D_PG$Date[96:228] , D_PG$StockPrice[96:228], type = "l", col="green")
abline(v = as.Date("1983-01-01") , col = "blue")
```
#Coca-Cola was going up, while Procter and Gamble was going down.

(b) In the time period shown in the plot, which stock generally has lower values?
```{r}
plot(D_CC$Date[96:228] , D_CC$StockPrice[96:228], type = "l", col="black", xlab = ("Date") , ylab = ("StockPrice"))
lines(D_PG$Date[96:228] , D_PG$StockPrice[96:228], type = "l", col="green")
```
#Coca-Cola

<br><hr>

###  Section-3 Visualizing Stock Dynamics 1995-2005

__§ 3.1__ Which stock fell the most right after the technology bubble burst in March 2000?
```{r}
plot(D_CC$Date[300:432] , D_CC$StockPrice[300:432], type = "l", col="black" , ylim = c(0 , 200), xlab = ("Date") , ylab = ("StockPrice"))
lines(D_B$Date[300:432] , D_B$StockPrice[300:432], type = "l", col="red")
lines(D_GE$Date[300:432] , D_GE$StockPrice[300:432], type = "l", col="brown")
lines(D_IBM$Date[300:432] , D_IBM$StockPrice[300:432], type = "l", col="orange")
lines(D_PG$Date[300:432] , D_PG$StockPrice[300:432], type = "l", col="green")
abline(v = as.Date("2000-03-01") , col = "blue")
```
#General Electric (GE)

__§ 3.2__ Which stock reaches the highest value in the time period 1995-2005?
```{r}
plot(D_CC$Date[301:432] , D_CC$StockPrice[301:432], type = "l", col="black" , ylim = c(0 , 200), xlab = ("Date") , ylab = ("StockPrice"))
lines(D_B$Date[301:432] , D_B$StockPrice[301:432], type = "l", col="red" , ylim = c(0 , 200))
lines(D_GE$Date[301:432] , D_GE$StockPrice[301:432], type = "l", col="brown" , ylim = c(0 , 200))
lines(D_IBM$Date[301:432] , D_IBM$StockPrice[301:432], type = "l", col="orange" , ylim = c(0 , 200))
lines(D_PG$Date[301:432] , D_PG$StockPrice[301:432], type = "l", col="green" , ylim = c(0 , 200))

```
#IBM

__§ 3.3__ In October of 1997, there was a global stock market crash that was caused by an economic crisis in Asia. Comparing September 1997 to November 1997, which companies saw a decreasing trend in their stock price? (Select all that apply.)
```{r}
library(ggplot2)
ggplot(filter(alldata,Date>="1997-09-01"&Date<="1997-11-30"),aes(x=Date,y=StockPrice,colour=company))+
  geom_line()
```
#Boeing

__§ 3.4__ In the last two years of this time period (2004 and 2005) which stock seems to be performing the best, in terms of increasing stock price?
```{r}
ggplot(filter(alldata,Date>="2004-01-01"&Date<="2005-12-31"),aes(x=Date,y=StockPrice,colour=company))+
  geom_line()
```
#Boeing

<br><hr>


###  Section-4 Monthly Trends

__§ 4.1__ For IBM, compare the monthly averages to the overall average stock price. In which months has IBM historically had a higher stock price (on average)? Select all that apply.
```{r}
sort(tapply(D_IBM$StockPrice,months(D_IBM$Date),mean),decreasing = T)
mean(D_IBM$StockPrice)
```
#二月

__§ 4.2__ General Electric and Coca-Cola both have their highest average stock price in the same month. Which month is this?
```{r}
sort(tapply(D_GE$StockPrice,months(D_GE$Date),mean),decreasing = T)
sort(tapply(D_CC$StockPrice,months(D_CC$Date),mean),decreasing = T)
```
#四月

__§ 4.3__ For the months of December and January, every company's average stock is higher in one month and lower in the other. In which month are the stock prices lower?
```{r}
tapply(D_B$StockPrice,months(D_B$Date),mean)
```
#十二月

<br><br><br>

